### 2017-07-07 paper.tex
Adding more material on learning objectives.
Closes #31.

Rather than itemizing prior knowledge and learning objectives,
it can be helpful to write \emph{learner profiles} to clarify
the learner's general background,
what they already know,
what \emph{they} think they want to do,
how the material will help them,
and any special needs they might have.
This technique is borrowed from user interface design,
and a typical learner profile is presented in Box~1.

@@

One way to achieve this is to take existing courses and break them down into smaller, single-purpose modules
(a change which has pedagogical and administrative advantages in its own right).
When this is done,
these modules can be made more discoverable
by referencing specific points in the model curricula promulgated by many professional societies.
Smaller modules are also more approachable for new contributors (\ruleref{empower}).

@@

Pre- and post-class surveys should be used to uncover larger issues,
particularly those arising from developers not fully understanding their audience,
e.g.,
assuming prior knowledge that learners do not have.
Post-class surveys are most effective when conducted 30--90 days after class;
this gives people time to reflect,
so their feedback will more accurately reflect what they learned
rather than how entertained they were.

>>>>

Instead of starting with learning objectives (\ruleref{practices}),
it can be helpful to write \emph{learner profiles} to clarify
the learner's general background,
what they already know,
what \emph{they} think they want to do,
how the material will help them,
and any special needs they might have.
This technique is borrowed from user interface design,
and a typical learner profile is presented in Box~1.

@@

One way to achieve this is to take existing courses and break them down into smaller, single-purpose modules
(a change which has pedagogical and administrative advantages in its own right).
When this is done,
these modules can be made more discoverable
by referencing specific points in the model curricula promulgated by many professional societies
(e.g., as learning objectives).
Smaller modules are also more approachable for new contributors (\ruleref{empower}).

@@

Pre- and post-class surveys and interviews should be used to uncover larger issues,
particularly those arising from developers not fully understanding their audience,
e.g.,
assuming prior knowledge that learners do not have.
Post-class surveys are most effective when conducted 30--90 days after class;
this gives people time to reflect,
so their feedback will more accurately reflect what they learned
rather than how entertained they were.
Clearly-stated learning objectives (\ruleref{practices}) are essential here,
as they tell assessors what they should be measuring.
